Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-23 article/article.Rmd
Commit 2024-06-23 18:14

The magnitude of the ECE events does not exceeds the values reported for sites with
more favourable conditions for the phenomenon. The climatological characteristic of
the ECE events, showed that the most active months are spread on half of the year
(March -- June and September and October).  We found that CE conditions, can have a
duration of more than an hour in rare cases, with the bulk of the cases having a
duration under 5 minutes.  Some of the characteristics of CE and ECE events we
analysed,
have strong similarities with results
by @Vamvakas2020, for a city southern of Thessaloniki, with the analogues differences on the
 intensity of the solar radiation.

An interpretation of the CE trends, shows that the interaction of GHI with the
clouds,
through this 30 year period, is a dynamic phenomenon that's needs further investigation.
Although, to approach it, we need more long-term observations of AOD and clouds
characteristics.

>>>>

The magnitude of the ECE events does not exceed the values reported for sites with
more favourable conditions for the phenomenon. The climatological characteristic of
the ECE events, showed that the most active months are spread in half of the year
(March -- June, September and October). We found that CE conditions, can have a
duration of more than an hour in rare cases, with the bulk of the cases having a
duration under 5 minutes.  Some of the characteristics of CE and ECE events we
analysed have strong similarities with results by @Vamvakas2020 for the city of
Patras, south of Thessaloniki, with analog differences on the intensity of the
solar radiation.

An interpretation of the CE trends shows that the interaction of GHI with the clouds,
through this 30 year period, is a dynamic phenomenon that needs further
investigation.  Although, to approach it, we need more long-term observations of AOD
and clouds characteristics.

<!-- END -->
